---
title: "BST650_Regression_Assign3"
author: "Nina Dyatchenko"
date: "December 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup
We load the packages and data we need:

```{r}
library(tidyverse)
wcgs_df <- read_csv("C:/Users/Nina/Documents/GitHub/BST650_Regression/wcgs.csv")
```

Now we can construct the linear model in order to test the assumptions above.
 
```{r}
chol_mod <- lm(chol ~ age + weight + sbp, data = wcgs_df)
```
## Assumptions of Multiple Linear Regression
### Assumption 1: Model Errors are Normally Distributed
Overall, the residuals appear to be normally distributed, based on the 
histogram, but we may have a few outliers. When we inspect the QQ-plot, 
we probably have an outlier.
```{r}
str(chol_mod)
# Histogram
hist(chol_mod$residuals)
 # QQ-Plot
qqnorm(chol_mod$residuals)
qqline(chol_mod$residuals)
```
 Try a transformation:
```{r}
hist(wcgs_df$chol)
cholSq_mod <- lm(sqrt(chol) ~ age + weight + sbp, data = wcgs_df)
hist(cholSq_mod$residuals)
 qqnorm(cholSq_mod$residuals)
qqline(cholSq_mod$residuals)
```
That's probably not any better. Let's leave the data alone...
 
### Assumption 2: Model Errors are Centred at 0
The quick and dirty way would be to look at the centre of the histogram. We can 
also perform a statistical test:

```{r}
t.test(chol_mod$residuals, alternative = "two.sided", mu = 0)
```

 0 is dead-set in the middle of the confidence interval. We're rather confident 
 that the mean of the residuals is close enough to 0.
 
### Assumption 3: Model Errors are Homoscedastic (equal variance).

```{r Assumption 3}
plot(chol_mod)
```
Scale-Location (or Spread-Location). Used to check the homogeneity of variance of the residuals (homoscedasticity). Horizontal line with equally spread points is a good indication of homoscedasticity. 

### Assumption 4: Model Errors are Independent.


### Assumption 5: Model Predictors are not Perfectly Correlated

```{r}
cor(wcgs_df$age, wcgs_df$weight)
cor(wcgs_df$age, wcgs_df$sbp)
cor(wcgs_df$weight, wcgs_df$sbp)
```
The values are below 0.26 so the age, weight, and sbp are not highly correlated.